A Lattice Boltzmann Method for immiscible multiphase flow simulations using the Level Set Method

### 2015-08-17 Vortrag/folien.tex
Nochmals Folien. Letztes Update für heute.

\begin{frame}
\frametitle{Multiphase flow - Examples}
\begin{itemize}
\item<1-> Examples
\item<2-> e.g. Oil in water 
\item<3-> \ldots
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Interface capturing}
Hydrodynamics are solved by LBM.
\begin{itemize}
\item<1-> Interface becomes a new boundary condition for LBM
$$f_i(x,t+1) = f_{i^*}^{+}(x,t) + 6hf_{i}^{*}c_i \cdot \tilde{u} + R_i$$
\item<2-> $\tilde{u}$ is the velocity on the interface along the direction $c_i$
\item<3-> $R_i$ ensures the jump conditions of the normal stress and corrects the error terms resulting from the bounce back treatment
\end{itemize}
TODO: Bild vom Interface
<Coupling und BC's erklären!!\ldots>
\end{frame}

\begin{frame}
$\tilde{u}$ is calculated by linear interpolation:
$$\tilde{u} = q u (x_2,t) + (1-q) u(x_1,t)$$
$R_i$ consists of several parts:
$$R_i = 6 h^2 f_{i}^{*} {\Lambda}_i : A$$
\begin{itemize}
\item<1-> with:
$$ {\Lambda}_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbb{I}$$
$$ A = -q(1-q)[S] - (q - 1/2) S^{2} + O(h)$$
\item<2-> $S^{(k)}$ velocity gradient at $x_k$
\item<3-> $[S]$ jump of velocity gradient at the interface. Depends on normal, tangent and curvature.
\end{itemize}
\end{frame}

@@

\section{Results}
\begin{frame}
\frametitle{Validation}
\framesubtitle{Validation setups}
\end{frame}

\section{Outlook}
\begin{frame}
\frametitle{Conclusion \& Outlook}
$\rightarrow$ \dots

\vspace{.8cm}
Outlook:
\begin{itemize}
\item<1-> Add correction term to prevent mass loss
\item<1-> Reduce computational effort: Store Level-Set function only in narrow band around interface, Adalsteinsson and Sethian
TODO: Quellen als Footnotes + Uebersichtsfolie
\item<2-> Include thermal flow (simulate e.g. lava lamp) / Include gravity
\item<3-> \dots
\end{itemize}

@@

\begin{frame}
\frametitle{References}
\begin{thebibliography}{etw}
   \bibitem{thoemmes}
     Thömmes, Guido, et al. "A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method." Journal of Computational Physics 228.4 (2009): 1139-1156
\end{thebibliography}
\end{frame}

>>>>

\begin{frame}
\frametitle{Multiphase flow}
Examples
\begin{itemize}
\item<1-> Liquid-liquid mixtures (e.g. oil in water) 
\item<2-> Gas-liquid mixtures (e.g. bubble dynamics)
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Mathematic foundation}
\framesubtitle{Interface capturing}
Hydrodynamics are solved by LBM.
\begin{itemize}
\item<1-> Interface becomes a new boundary condition for LBM
$$f_i(x,t+1) = f_{i^*}^{+}(x,t) + 6hf_{i}^{*}c_i \cdot \tilde{u} + R_i$$
\item<2-> $\tilde{u}$ is the velocity on the interface along the direction $c_i$
\item<3-> $R_i$ ensures the jump conditions of the normal stress and corrects the error terms resulting from the bounce back treatment
\end{itemize}
TODO: Bild vom Interface (sowas wie Fig.1-Right im Paper)
\end{frame}

\begin{frame}
\visible<1->{
$\tilde{u}$ is calculated by linear interpolation:
$$\tilde{u} = q u (x_2,t) + (1-q) u(x_1,t)$$
}
\visible<2->{
$R_i$ consists of several parts:
$$R_i = 6 h^2 f_{i}^{*} {\Lambda}_i : A$$
}
\visible<3->{
\begin{itemize}
\item<3-> with:
$$ {\Lambda}_i = c_i \otimes c_i - \frac13 {|c_i|}^2 \mathbb{I}$$
$$ A = -q(1-q)[S] - (q - 1/2) S^{2} + O(h)$$
\item<4-> $S^{(k)}$ velocity gradient at $x_k$
\item<5-> $[S]$ jump of velocity gradient at the interface. Depends on normal, tangent and curvature.
\end{itemize}
}
\end{frame}

@@

\section{Results}
\begin{frame}
\frametitle{Validation}
TODO: Hier könnte man Bilder von unserer ersten Simulation zeigen. Leider können wir die Richtigkeit bisher nicht mit Zahlen belegen.
\framesubtitle{Validation setups}
\end{frame}

\section{Outlook}
\begin{frame}
\frametitle{Outlook}
$\rightarrow$ \textit{Conclusion habe ich rausgenommen. Ich wüsste zumindest nicht was wir da reinschreiben könnten. Wenn du was weißt, darfst du das aber sehr gerne wieder einfügen.}

\vspace{.8cm} 
Outlook:
\begin{itemize}
\item<1-> Add correction term to prevent mass loss
\item<2-> Reduce computational effort: Store Level-Set function only in narrow band around interface, Adalsteinsson and Sethian
TODO: Quellen als Footnotes + Uebersichtsfolie
\item<3-> Include thermal flow (simulate e.g. lava lamp) / Include gravity
\end{itemize}

@@

\begin{frame}
\frametitle{References}
\begin{thebibliography}{etw}
   \bibitem{thoemmes}
     Thömmes, Guido, et al. "A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method." Journal of Computational Physics 228.4 (2009): 1139-1156
   \bibitem{mitchell}
     Mitchell, Ian, A Toolbox of Level Set Methods
\end{thebibliography}
\end{frame}
